::: {.lang .es}
# Computación e Inteligencia
¡Bienvenidos al curso de **Computación e Inteligencia**!

Este sitio contiene todos los materiales del laboratorio para el curso. Aquí encontrarás:

- Laboratorios prácticos
- Ejercicios interactivos  
- Recursos adicionales

### Navegación

- **Labs**: Contiene todos los laboratorios del curso
- **🌐**: Cambia entre Español e Inglés

### Laboratorios

<div class="row">
```{r results='asis'}
labs <- quarto::from_yaml("_labs.yml")
for (lab in labs) {
  cat(sprintf('
  <div class="col-md-4">
    <div class="card mb-4">
      <div class="card-body">
        <h5 class="card-title">%s</h5>
        <p class="card-text">%s</p>
        <a href="%s" class="btn btn-primary">Ir al Laboratorio</a>
      </div>
    </div>
  </div>
  ', lab$title$en, lab$description$en, lab$link))
}
```
</div>
:::

::: {.lang .en}
# Computation and Inteligence
Welcome to the **Computation and Intelligence** course!

This site contains all the laboratory materials for the course. Here you'll find:

- Practical laboratories
- Interactive exercises
- Additional resources

### Navigation

- **Labs**: Contains all course laboratories
- **🌐**: Switch between Spanish and English

### Labs

<div class="row">
```{r results='asis'}
labs <- quarto::from_yaml("_labs.yml")
for (lab in labs) {
  cat(sprintf('
  <div class="col-md-4">
    <div class="card mb-4">
      <div class="card-body">
        <h5 class="card-title">%s</h5>
        <p class="card-text">%s</p>
        <a href="%s" class="btn btn-primary">Go to Lab</a>
      </div>
    </div>
  </div>
  ', lab$title$en, lab$description$en, lab$link))
}
```
</div>
:::